graphsim: An R package for simulating gene expression data from graph structures of biological pathways

### 2020-06-01 paper/paper.Rmd
restore data for TGFBeta-Smad pathway

```{r, eval = FALSE}
#install packages required (once per machine)
install.packages("graphsim")

```
```{r, warning=FALSE, results='hide', message=FALSE}
#load required packages (once per R instance)
library("graphsim")
#load packages for examples
library("igraph"); library("gplots"); library("scales")
```

>>>>

```{r, eval = FALSE}
#install packages required (once per machine)
install.packages("graphsim")
```
```{r, warning=FALSE, results='hide', message=FALSE}
#load required packages (once per R instance)
library("graphsim")
#load packages for examples
library("igraph"); library("gplots"); library("scales")
```
